% \listfiles
\documentclass{res}
\usepackage[dvipsnames]{xcolor}
\usepackage[sc]{mathpazo}
\linespread{1.05}         % Palladio needs more leading (space between lines)
\usepackage[T1]{fontenc}

\usepackage{amssymb}
\usepackage[hidelinks]{hyperref}
\pagestyle{empty}

\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\topmargin=-0.5in % start text higher on the page

\def\ctitle#1#2#3{\emph{\textcolor{Maroon}{#1}}\hfill#2 --- #3 \smallskip\\}

\usepackage[sorting=ynt,maxbibnames=10]{biblatex}
\addbibresource{cryptobib/abbrev3.bib}
\addbibresource{cryptobib/crypto.bib}

\begin{document}
\moveleft.5\hoffset\centerline{\Large\bf Junwei WANG}
\moveleft\hoffset\vbox{\hrule width\resumewidth}\smallskip
\moveleft.5\hoffset\centerline{41 Boulevard des Capucines}
\moveleft.5\hoffset\centerline{75002 Paris, France}
\moveleft.5\hoffset\centerline{\href{mailto:junwei.wang@cryptoexperts.com}{junwei.wang@cryptoexperts.com}}
\moveleft.5\hoffset\centerline{(+33) 7 69 39 52 85}
\moveleft.5\hoffset\centerline{\href{https://jwa.ng}{https://jwa.ng}}
\newcommand\ignore[1]{}


\begin{resume}

\section{\large \centerline{EDUCATION}}
\bigskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ctitle{Ph.D. in Cryptography}{April 2017}{June 2020}
\textbf{University of Luxembourg}, Esch-sur-Alzette, Luxembourg\\
\textbf{University Paris 8}, Saint-Denis, France
\smallskip \\
Thesis entitled \textsl{On the Practical Security of White-Box Cryptography}, under the supervision of
Prof.\ \href{http://www.crypto-uni.lu/jscoron/index.html}{Jean-S\'{e}bastien Coron},
Prof.\ \href{http://www.math.univ-paris13.fr/~mesnager/}{Sihem Mesnager},
Dr.\ \href{https://scholar.google.com/citations?user=xwzhjfoAAAAJ&hl=en}{Pascal Paillier},
and Dr.\ \href{http://www.matthieurivain.com/}{Matthieu Rivain}.
\bigskip \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ctitle{Master in Information and Computer Science}{September 2013}{September 2014}
\textbf{University of Luxembourg}, Luxembourg City, Luxembourg
\smallskip\\
Thesis entitled \textsl{Efficient Implementation of High-Order DPA Countermeasures for the AES
  using the ARM NEON Instruction Set}, under the supervision of
Prof.\ \href{http://www.crypto-uni.lu/jscoron/index.html}{Jean-S\'{e}bastien Coron}.
\bigskip \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ctitle{Master of Computer Science and Technology}{September 2012}{June 2015}
\textbf{Shandong University}, Jinan, China
\bigskip\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ctitle{Bachelor of Software Engineer}{September 2008}{June 2012}
\textbf{Shandong University}, Jinan, China
\bigskip

\section{\large\centerline{WORKING EXPERIENCE}}
\bigskip
\ctitle{Cryptography Experts}{July 2020}{\hspace{1.5cm}}
\textbf{CryptoExperts}, Paris, Paris
\smallskip \\
Research \& develop technology on white-box cryptography and privacy-preserving cryptography.
Management of IT infrastructure.
\bigskip\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ctitle{Cryptography Engineer}{April 2017}{June 2020}
\textbf{CryptoExperts}, Paris, Paris
\smallskip \\
Research on white-box cryptography. Develop white-box technology and distributed system for
white-box generations.
\bigskip\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ctitle{Research Intern}{April 2018}{July 2018}
\textbf{Riscure B.V.}, Delft, the Netherlands
\smallskip\\
Research on attacks in white-box cryptography.
\bigskip\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ctitle{Senior Software Engineer}{July 2015}{April 2017}
\textbf{Baidu Inc.}, Beijing, China
\smallskip\\
Design and develop systems for efficient production of knowledge graph data.
\bigskip\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ignore{
In charge of the workflow of creating knowledge graphs by processing of web
crawled data in the Searching Service Group, including,
\begin{itemize}[\itemsep=-2pt]
  \item Developing and maintaining a cleanse system (based on open source
    code) dealing with messy data: cleaning, transforming and extending it;
  \item Developing and maintaining the platform designing for R\&D engineers
    and outsourced staffs to build meaningful knowledge graphs inspired by
    structured or semi-structured data;
  \item Developing an adapter system to match the interfaces between the
    crawling system and its downstream systems, etc.
  \end{itemize}
}
% \ctitle{R\&D Engineer (Intern)}{December 2014}{May 2015}
% \textbf{Eyespage}, Beijing, China \\\vspace{-3.5pt}
% \begin{itemize}  \itemsep -1pt
%   \item Designed and developed the API.
%   \item Developed a spider to crawl data from Google Play Store by using the
%     Scrapy framework.
%   \item Operated and monitored with Elastic-Logstash-Kibana stack, Zabbix and
%     so on.
%   \item Co-designed the system architecture.
% \end{itemize}
%\medskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ctitle{R\&D Engineer (Intern)}{August 2011}{January 2012}
\textbf{Baidu Inc.}, Beijing, China
\smallskip\\
Developed a monitoring and warning system for online services of Baidu, mainly focusing on obtaining, processing and displaying data.
\bigskip\\

\section{\large\centerline{PROAGRAM COMMITTEE MEMBER}}
~
\begin{itemize}
\item TCHES 2022
\item CHES 2021 Artifact
\item \href{https://icsp.co.in/}{ICSP 2021}
\end{itemize}
\bigskip

\section{\large\centerline{EVENT ORGANIZATION}}
~

\begin{itemize}
\item Co-organizer of the CHES 2021 Challenge. The WhibOx Contest – Edition 3.
\item Co-organizer of the CHES 2019 Challenge. The WhibOx Contest – Edition 2.
\end{itemize}
\bigskip

\section{\large\centerline{PUBLICATIONS}}
\bigskip

\hphantom{\cite{TCHES:GouRivWan20}~\cite{JCEng:GPRW20}~\cite{EPRINT:GPRW18}~\cite{COSADE:BRVW19}~\cite{RSA:WVGX15}} \printbibliography[heading=none,title=~]

\end{resume}

\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
