% \listfiles
\documentclass{res}
\usepackage[dvipsnames]{xcolor}
\usepackage[sc]{mathpazo}
\linespread{1.05}         % Palladio needs more leading (space between lines)
\usepackage[T1]{fontenc}

\usepackage{amssymb}
\usepackage{hyperref}
\pagestyle{empty}

\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
%\rhead{ {\it J. Wang}\\{\it p. \thepage} } % put text in header (right side)
%\cfoot{}                                     % the foot is empty
\topmargin=-0.5in % start text higher on the page

\def\ctitle#1#2#3{\emph{\textcolor{Maroon}{#1}}\hfill#2 - #3 \smallskip\\}

\usepackage{biblatex}
\addbibresource{cryptobib/abbrev3.bib}
\addbibresource{cryptobib/crypto.bib}


\begin{document}
\moveleft.5\hoffset\centerline{\Large\bf Junwei WANG}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
\moveleft.5\hoffset\centerline{2 All\'ee Joseph Lalande}
\moveleft.5\hoffset\centerline{94000 Cr\'eteil, France}
\moveleft.5\hoffset\centerline{\href{mailto:i.junwei.wang@cryptoexperts.com}{i.junwei.wang@cryptoexperts.com}}
\moveleft.5\hoffset\centerline{(+33) 7 69 39 52 85}
\newcommand\ignore[1]{}

\begin{resume}

\section{\large \centerline{\'EDUCATION}}
\bigskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ctitle{Candidat au doctorat en informatique}{avril 2017}{juillet 2020 (attendu)}
\textbf{CryptoExperts SAS}, \`a Paris, France \\
\textbf{University of Luxembourg}, \`a Esch-sur-Alzette, Luxembourg\\
\textbf{University Paris 8}, \`a Saint-Denis, France
\smallskip \\
Je travaille sur la cryptographie en boîte blanche.
Ma thèse est sous la direction de
Prof. \href{http://www.crypto-uni.lu/jscoron/index.html}{Jean-S\'{e}bastien Coron},
et Prof. \href{http://www.math.univ-paris13.fr/~mesnager/}{Sihem Mesnager},
et Dr. \href{https://scholar.google.com/citations?user=xwzhjfoAAAAJ&hl=en}{Pascal Paillier},
et Dr. \href{http://www.matthieurivain.com/}{Matthieu Rivain}.
Je reçois un financement du projet ANR.
\bigskip \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ctitle{Master en informatique}{septembre 2012}{juin 2014}
\textbf{University of Luxembourg}, \`a Luxembourg, Luxembourg\\
\textbf{Shandong University}, \`a Jinan, Chine
\smallskip\\
Thèse intitulée \guillemotleft{}\emph{Efficient Implementation of High-Order DPA
Countermeasures for the AES using the ARM NEON Instruction Set}\guillemotright{},
sous la direction de
Prof. \href{http://www.crypto-uni.lu/jscoron/index.html}{Jean-S\'{e}bastien Coron}.
\bigskip \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ctitle{Diplôme d'ing\'enieur}{septembre 2008}{juin 2012}
\textbf{Shandong University}, \`a Jinan, Chine
\bigskip

\section{\large\centerline{\textsc{EXP\'ERIENCE DE TRAVAIL}}}
\bigskip
\ctitle{Stagiaire de recherche}{avril 2018}{juillet 2018}
\textbf{Riscure B.V.}, \`a Delft, les Pays-Bas
\medskip\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ctitle{Ing\'enieur senior}{juillet 2015}{avril 2017}
\textbf{Baidu Inc.}, \`a Beijing, Chine
\smallskip\\
J'\'etais au d\'epartement Knowledge Graph.
Mon travail consistait \`a concevoir et d\'evelopper des syst\`emes pour
production de donn\'ees sur les connaissances.
\medskip\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ignore{
In charge of the workflow of creating knowledge graphs by processing of web
crawled data in the Searching Service Group, including,
\begin{itemize}  \itemsep -2pt
  \item Developing and maintaining a cleanse system (based on open source
    code) dealing with messy data: cleaning, transforming and extending it;
  \item Developing and maintaining the platform designing for R\&D engineers
    and outsourced staffs to build meaningful knowledge graphs inspired by
    structured or semi-structured data;
  \item Developing an adapter system to match the interfaces between the
    crawling system and its downstream systems, etc.
  \end{itemize}
}
\ignore{
\ctitle{Stagiaire de recherche et de d\'eveloppement}{d\'ecembre 2014}{mai 2015}
\textbf{Eyespage}, Beijing, China %\vspace{-3.5pt}
\begin{itemize}  \itemsep -1pt
  \item Designed and developed the AI.
  \item Developed a spider to crawl data from Google Play Store by using the
    Scrapy framework.
  \item Operated and monitored with Elastic-Logstash-Kibana stack, Zabbix and
    so on.
  \item Co-designed the system architecture.
\end{itemize}
\medskip\\%
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ctitle{Stagiaire de recherche et de d\'eveloppement}{ao\^ut 2011}{janvier 2012}
\textbf{Baidu Inc.}, \`a Beijing, China
\ignore{
\begin{itemize}  \itemsep -2pt
  \item Developed a ``user friendly" monitoring and warning system for
    online services of Baidu, mainly focusing on obtaining, processing and
    displaying data.
\end{itemize}
}

\ignore{
\section{COMPUTER \\ SKILLS}
{\sl Languages \& Software:} C, C++, PHP, Perl, Java, ARM NEON Assembly,
Python, Shell Script, Scala   Vim, MySQL, Matlab/Octave, LAMP and so on. \\
{\sl Operating Systems:} Linux.
}

\ignore{

\vspace{0.2in}
\section{\centerline{COMPUTER SKILLS}}
\vspace{15pt}
\begin{itemize}
  \item Solid skills in programming, especially in Java and Python programming
    languages, also using Shell Scripts, PHP, C, C\verb!++!, Perl, Scala, ARM
    NEON Assembly;
  \item Familiar with Unix-like operating systems;
  \item Familiar with distributed computing frameworks, e.g., Hadoop, HBase and
    Kafka;
  \item Familiar with popular relational database and NoSql databases, e.g.,
    MySql, Redis, Elasticsearch and so on.
  \end{itemize}
  }


\ignore{
\vspace{0.2in}
\section{\centerline{WEBSITES}}
\vspace{15pt}
\begin{itemize}
\item {\bf Homepage} http://junwei.co
\item {\bf Github} https://github.com/junwei-wang
\item {\bf LinkedIn} https://www.linkedin.com/in/junweiwang
\end{itemize}
}

\section{\large\centerline{PUBLICATIONS}}
\bigskip


\hphantom{\cite{COSADE:BRVW19}
\cite{RSA:WVGX15}
\cite{TCHES:RivWan19}
\cite{EPRINT:GPRW18}}
\printbibliography[heading=none,title=~]


\vspace{0.2in}
\section{\large \centerline{LANGUES}}
\vspace{15pt}
\begin{itemize}
\item \textbf{Chinois} (\emph{mother tongue})
\item \textbf{Anglais} (\emph{comp\'etence professionnelle})
\item \textbf{Fran\c cais} (\emph{comp\'etence acquise de niveau A2.1})
\end{itemize}

\end{resume}

\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
